---
title: "GitHub for Collaboration"
output: 
  html_document: 
    keep_md: yes 
---
```{r, message=FALSE, warning=FALSE}
library(fivethirtyeight)
library(tidyverse)
library(moderndive)
library(ggplot2)
library(ggridges)
library(ggmosaic)
```
#Avengers

#Gender VS. First Death
```{r, message=FALSE, warning=FALSE}
ggplot(data = avengers) +
  geom_bar(aes(x = gender, fill = death1))
```
```{r}
avengers %>% 
  count(gender)
```

In this graph, Male appear to have more occurences of dying for the first time than females do. The maximum number of males is almost doubled of the number of females. 


# Honarary Status VS. Firsh Death
```{r, message=FALSE, warning=FALSE}
ggplot(data = avengers) +
  geom_bar(aes(x = honorary, fill = death1))
```
Those who have a full honorary status has high occurence of first death than other categories.

#Gender VS. Honorary Status 
```{r, message=FALSE, warning=FALSE}
ggplot(data = avengers) +
  geom_mosaic(aes(x = product(factor(gender), honorary), fill = factor(gender))) +
  theme_minimal()
```

```{r, message=FALSE, warning=FALSE}
ggplot(data=avengers) +
  geom_bar(mapping = aes(x=honorary, fill=factor(gender)), position = "dodge") +
  scale_fill_discrete("Gender") +
  facet_wrap(~gender, ncol = 1)
```
In the full category, males are more represented than females. for probationary, there's only male representitive. Academy has almost even split. For honorary, males has more representitive than female.


