---
title: "Complaints about emergency room doctors "
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(faraway)
library(tidyverse)
library(ggridges)
```


# Preliminary analysis 
Dataset has 44 doctors serveyed in 1998. Variables examined are *visits*, *complaints*, *residency*, *gender*, *revenue*, and *hours*. We are trying to determine whether visits, gender, revenue, and hours worked predict number of complaints received. 

```{r}
ggplot(data=esdcomp)+
  geom_boxplot(aes(x=visits, y=complaints, color=gender))
```

* Women have less visists than men 
* Median number of complaints are similar for both gender 
* Upper quartile for complaints for men is larger than that of women  -- there is more variation in complaints for men, data is skewed right, higher maximum 
* Possible reasons:
  + more visits = more patients that could complain = working more hours (tired and slack -> get complains) 
  + less female doctors 

\

```{r}
ggplot(data=esdcomp)+
  geom_bar(aes(x=gender))
```

* Less female doctors 

\

```{r}
ggplot(data=esdcomp)+
  geom_boxplot(aes(x=gender, y=revenue))
```

* Females make less revenue 
* More variation in male revenue 
* Maximum for male is a lot higher than that of women 

\

```{r}
ggplot(data=esdcomp)+
  geom_boxplot(aes(x=visits, y=hours, color=gender))
```

* Women have less visits but worked more hours than men 
* Median for both genders are very similar 
* Minimum for men's working hour is higher than that of women's 

\

```{r}
ggplot(data=esdcomp)+
  geom_boxplot(aes(x=complaints, y=hours, color=gender))
```

* Women get less complaints but work more hours, slightly more variation 
* Men work more hours to begin with thus have more complaints

\

```{r,  warning=FALSE, message=FALSE}
ggplot(data=esdcomp)+
  geom_density_ridges(aes(x=revenue, y=gender, fill=gender))
```

* There is a more even distribution of revenue for male doctors than for female doctors 
* Men make more in general (min and max)
* Women's median income is 250, men is closer to 260/270. 

\
\
\
\
\

# STEP FORWARD
See how the results come out then decided if we do a interaction effect 

(@) lm model: complaints ~ visits + hours 
(@) lm model: complaints ~ visits + hours + gender 
(@) lm model: complaints ~ gender + revenue 
(@) find R^2 for all models and explain in terms of the dataset 
(@) summarize results 
(@) talk about variables that we wished we had 
(@) implications of the dataset and our prediction 



